---
title: "Lab 1: Intro to R"
author: "Adnan Hussein"
date: "`r Sys.Date()`"
output: openintro::lab_report
---

Loading dependencies
```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro)
```

# Dr. Arbuthnot’s Baptism Records
The number of columns is 3
The number of Row is 82
```{r}
glimpse(arbuthnot)
```

Closer look at Arbuthnot
```{r}
arbuthnot$boys
```

# Data visualization
Data visualization
```{r}
ggplot(data = arbuthnot, aes(x = year, y = girls)) + 
  geom_point()
```

Different graph
```{r}
ggplot(data = arbuthnot, aes(x = year, y = girls)) +
  geom_line()
```

Graphing help
```{r}
?ggplot
```

# R as a big calculator
Doing basic math
```{r}
5218 + 4683
```

Calculating the sum
```{r}
arbuthnot$boys + arbuthnot$girls
```

# Adding a new variable to the data frame
```{r}
arbuthnot <- arbuthnot %>%
  mutate(total = boys + girls)
```

Glimpse the new column
```{r}
glimpse(arbuthnot$total)
```

Graphing the new total
```{r}
ggplot(data = arbuthnot, aes(x = year, y = total)) + 
  geom_line()
```

New ratio column
```{r}
arbuthnot <- arbuthnot %>%
  mutate(boy_to_girl_ratio = boys / girls)
```

Glimpse the new ratio column
```{r}
glimpse(arbuthnot$boy_to_girl_ratio)
```

New more boys than girls column
```{r}
arbuthnot <- arbuthnot %>%
  mutate(more_boys = boys > girls)
```

Glimpse the new more boys than girls column
```{r}
glimpse(arbuthnot$more_boys)
```

# More Practice
Summarize column: boys
```{r}
arbuthnot %>%
  summarize(min = min(boys),
            max = max(boys)
            )
```

Summarize column: girls
```{r}
arbuthnot %>%
  summarize(min = min(girls),
            max = max(girls)
            )
```

